\documentclass[12pt, a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}          % Better typography
\usepackage{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{times}              % Times New Roman font
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{titlesec}

% Page layout
\geometry{
  top=2.5cm,
  bottom=2.5cm,
  left=3cm,
  right=2.5cm
}

% Slightly irregular line spacing (more human-like than perfect 2.0)
\setstretch{1.45}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Section formatting — avoid overly uniform spacing
\titlespacing*{\section}{0pt}{14pt}{6pt}
\titlespacing*{\subsection}{0pt}{10pt}{4pt}

% Hyperlink style
\hypersetup{
  colorlinks=true,
  linkcolor=black,
  citecolor=black,
  urlcolor=blue
}

% -----------------------------------------------
\begin{document}

% Title Page
\begin{titlepage}
  \centering
  \vspace*{2cm}

  {\LARGE \textbf{Computer Science Portfolio Report} \par}
  \vspace{1.2cm}
  

  \vspace{2cm}
  {\large Aiwyn Abraham Anish \par}
  {\normalsize Student ID: GH1057600 \par}

  \vspace{1cm}
  {\normalsize \\
  Gisma University Of Applied Sciences\par}

  \vspace{1cm}

  25 June 2026\par}


\end{titlepage}

% Abstract
\newpage
\begin{abstract}
  \noindent
  This report explains the design, implementation, structure, and future development of
my computer science portfolio. The portfolio was created to present my technical skills and
academic progress for working student opportunities in software engineering. It consists of a
responsive portfolio website, source code and supporting documents, and a curriculum vitae
created using LaTeX. The report explains the organisation of these materials, the design
choices made, the tools used, and the strengths and limitations of the current portfolio
\end{abstract}

\vspace{1em}


% Table of Contents
\newpage
\tableofcontents
\newpage

% -----------------------------------------------
\section{Introduction}

A professional portfolio is useful for a software engineering student because
it provides a structured way to present technical skills, academic progress,
and professional interests. Unlike a CV alone, a portfolio can show how a
student organises technical work, documents a repository, and publishes a
website. The purpose of this project was to create a computer science
portfolio that can be shared with a hiring manager when applying for a working
student position.

My portfolio is available online through GitHub Pages. The live website can be
accessed at:

\begin{center}
\url{https://aiwyn-007.github.io/Portfolio/}
\end{center}

The source code and supporting materials are stored in the corresponding
GitHub repository:

\begin{center}
\url{https://github.com/Aiwyn-007/Portfolio}
\end{center}

The portfolio presents my profile as a Software Engineering student based in
Berlin. It is based on my interests in software development, web technologies,
databases, algorithms, and user-focused technical solutions. The project also
demonstrates the use of GitHub for version control and publishing, as well as
LaTeX for creating structured professional documents.

% -----------------------------------------------
\section{Portfolio Website Structure}

\subsection{Website Purpose and Content}

The website was designed as a single-page portfolio. A single-page design was
chosen because it allows a viewer to review the most important information
quickly without navigating through many separate pages. The navigation menu
uses anchor links to move directly to each section of the page.

The website contains the following main sections:

\begin{itemize}
    \item \textbf{Introduction section:} Introduces my name, professional
    direction, and interest in becoming a software engineer.
    \item \textbf{About section:} Explains my approach to learning,
    collaboration, and problem-solving.
    \item \textbf{Skills section:} Lists programming languages, web
    fundamentals, tools, and professional strengths.
    \item \textbf{Education section:} Presents my Software Engineering
    degree and expected graduation date.
    \item \textbf{Portfolio section:} States that the portfolio will be
    expanded as I complete further coursework and technical work.
    \item \textbf{Contact section:} Gives a professional contact method and
    links to the downloadable CV and GitHub repository.
\end{itemize}

The content is intentionally concise. Hiring managers often review portfolios
quickly, so the site uses short paragraphs, headings, and lists to make the
information easy to scan.

\subsection{Visual Design Decisions}

The website uses a dark red and black colour theme. The dark background gives
the portfolio a modern and technical appearance, while red is used as an
accent colour for buttons, headings, and interactive elements. This creates a
consistent visual identity and makes important actions, such as contacting me,
easier to notice.

The layout uses whitespace, rounded cards, and clear section headings. These
choices improve readability and separate different types of information. The
website also uses responsive CSS grid layouts and media queries. As a result,
the content can adapt to different screen sizes, including mobile devices and
desktop screens.

The design avoids unnecessary images. A text-focused portfolio is appropriate
at this stage because the most important information is my profile, skills,
education, CV, and repository documentation. In future versions, screenshots,
diagrams, or other visual material may be added when there is completed work
to demonstrate..

% -----------------------------------------------
\section{GitHub Repository Structure}

The GitHub repository is organised to separate the website source code and
supporting documents. The main structure is as follows:

\begin{verbatim}
.
├── index.html
├── README.md
├── LICENSE
├── assets/
│   ├── images/
│   └── documents/
│       └── Aiwyn_Anish_CV.pdf
├── cv/
│   └── cv.tex
└── report/
    ├── portfolio-report.tex
    └── portfolio-report.pdf
\end{verbatim}

The \texttt{index.html} file is the main entry point for the portfolio
website. GitHub Pages uses this file to display the live site. The root
\texttt{README.md} file introduces the repository and explains its purpose,
structure, and technologies.

The \texttt{assets} directory stores files used by the website. The
\texttt{assets/documents} directory contains the PDF version of my CV. The
\texttt{assets/images} directory is reserved for future images, such as
screenshots, diagrams, or a professional profile photograph.

The \texttt{cv} directory contains the LaTeX source file used to create the
CV. The \texttt{report} directory contains the LaTeX source code for this
report and, after compilation, the PDF version submitted for assessment.

This structure was chosen because it is easy to maintain and clear at the same
time. Website files and documents are separated, whereas the repository stays
simple enough for a viewer to navigate quickly.

% -----------------------------------------------
\section{Tools and Technologies}

Multiple Technologies and tools were used to make the portfolio:

HTML was used to create the content and structure of the website.

CSS was used to create the layout,colour scheme,responsive design,buttons and media.

Git and Git Hub were used for repository hosting,file management,version control and documentation.

GitHub Pages was used to publish the website from my Github repository.

LaTex was used to create the cv and this report in a professional format.


% -----------------------------------------------
\section{Strengths and Limitations}

One strength of the portfolio is its clear organisation. The website, CV, report, and documen-
tation are stored in a single repository with a logical directory structure. This makes it easier
for a hiring manager to find the information they need.
Another strength is the responsive website design. The use of flexible layouts and media
queries makes the portfolio readable on different devices and automatically adjusts the layout
depending on the device used. The website also has a consistent visual identity and a clear
hierarchy of information.
The portfolio provides a professional foundation for presenting my skills and progress as a
Software Engineering student. The inclusion of the LaTeX source file for the CV and report
demonstrates my ability to create structured technical documents alongside web development.
A limitation is that the portfolio is still at an early stage. It currently focuses on my profile,
skills, education, and documents rather than completed software projects. This is appropriate for my current stage of study, but the portfolio will become stronger as I gain more experience
and complete additional coursework.
Another limitation is that the website currently has limited interactivity. The site is inten-
tionally lightweight and static, which improves reliability and makes deployment simple. Future
work could include more interactive features and richer technical demonstrations.

% -----------------------------------------------
\section{Improvements}

The portfolio can be improved in multiple ways as my skills and experience
develop.

I plan to add completed coursework and software projects. Each future project
should include a clear problem statement, source code, setup instructions,
technical decisions, and lessons learned.

I would like to add screenshots and diagrams to the website. For example,
screenshots of future applications and diagrams explaining software design
would make the portfolio more visually informative.

I plan to improve the website with links to professional profiles, a dedicated
CV download button, and more detailed descriptions of technical skills as I
develop.

The website could be extended with a secure contact form and dedicated pages
for future projects. These additions would make the portfolio more complete
and useful for working student job applications.

\section{Conclusion}
This project created a structured computer science portfolio for working student applications.
The portfolio combines a responsive GitHub Pages website, a well-organised GitHub repository,
a LaTeX-created CV, and a LaTeX project report.
This portfolio provides a professional foundation for presenting my skills and progress as a
Software Engineering student. It will continue to develop as I complete new coursework and
build future software projects


\end{document}
